%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Conta Azul} % Organization
    {Joinville, SC, Brazil} % Location
    {Nov. 2019 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Acting as Security Engineer developing an Authentication solution.}
        \item {Involved with the LGPD (Data Protect Law) compliance team, developing audit tools.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {IFPB - Assert} % Organization
    {João Pessoa, Brazil} % Location
    {Abr. 2018 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Acting in different Projects/Clients and complexities.}
		\item {Build collaborative solutions for problem solving with the team.}
		\item {Editing User Manuals for Software solutions.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
      \cventry
        {Cofounder \& CTO} % Job title
        {Bubu Digital} % Organization
        {João Pessoa, Brazil} % Location
        {Jun. 2017 - Dec. 2017} % Date(s)
        {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Startup conceived from awarded HackBrazil/Microsoft Imagine Cup project.}
            \item {Startup pre-accelerated by Microsoft Instituto Innovaction}
            \item {Experience acquired on Business Management, Marketing, Entrepreneurism, and others.}
          \end{cvitems}
        }

%---------------------------------------------------------
  \cventry
    {Software Developer Intern} % Job title
    {Court of the State of Paraiba} % Organization
    {João Pessoa, Brazil} % Location
    {Oct. 2016 - Apr. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Intern allocated for web development.}
        \item {Work with web technologies and IaaS.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Software Developer Intern} % Job title
    {Digital Video Application Laboratory (Federal University of Paraiba)} % Organization
    {João Pessoa, Brazil} % Location
    {Sep. 2015 - Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Member of the team for development of digital television applications, sponsored by Brazilian Ministry of Culture.}
        \item {Innovative project, learning to work within short deadlines and high pressure.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {Digital Signal Processing Group (Fed. Inst. of Ed. Sci. and Technology of Paraiba)} % Organization
    {João Pessoa, Brazil} % Location
    {Feb. 2015 - Sep. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a software for postural analysis and body measurement.}
        \item {Built a Beowulf Cluster for Digital Image Processing.}
      \end{cvitems}
    }


%---------------------------------------------------------
\end{cventries}
