%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Chair, Treasurer, CoFounder, Student Member} % Affiliation/role
    {IFPB ACM (Association for Computing Machinery) Student Chapter} % Organization/group
    {Brazil} % Location
    {Jun. 2016 - Nov. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Develop the ability to run a student organization, writing reports, work in groups, recruit members and organizing events and activities.}      \end{cvitems}
    }
        
%---------------------------------------------------------
  \cventry
    {Chair, Founder, Student Member} % Affiliation/role
    {IFPB IEEE Computer Society Student Branch} % Organization/group
    {Brazil} % Location
    {Oct. 2018 - Sep. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
       \item {Develop the ability to run a student organization, writing reports, work in groups, recruit members and organizing events and activities.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Monitor, Competitor Member} % Affiliation/role
    {IFPB Informatics Olympiads Project (POP)} % Organization/group
    {Brazil} % Location
    {Apr. 2015 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Got the opportunity to teach how to solve computing problems to high school students.}
        \item {Participated on some problem solve competition and got good awards.}
        \item {Gained expertise in organizing problem solving competitions.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
    {Idealizer \& Staff}
    {TechKids}
    {João Pessoa, Brazil}
    {Ago. 2016 - PRESENT}
    {
      \begin{cvitems}
        \item {Social project to bring technology education in public schools for children}
        \item {More than 50 children benefited in test editions}
        \item {Main habilities developed: Execution Capability, Team Management, Sistemic Vision}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Volunteer, Student Member} % Affiliation/role
    {IFPB IEEE Women in Engineering Affinity Group} % Organization/group
    {Brazil} % Location
    {Apr. 2012 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
       \item {Contribute to the recruitment, engagement and empowerment of women in the STEAM fields.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Vice Chair, Membership Chairperson, Volunteer, Student Member} % Affiliation/role
    {IFPB IEEE Student Branch} % Organization/group
    {Brazil} % Location
    {Apr. 2012 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
         \item {Develop the ability to run a student organization, writing reports, work in groups, recruit members and organizing events and activities.}
      \end{cvitems}
    }
    
    
%---------------------------------------------------------
  \cventry
    {Team Leader, Commiter} % Affiliation/role
    {Mageia Linux - i18n pt\_BR Team} % Organization/group
    {Brazil} % Location
    {Apr. 2011 - 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Got the opportunity to work remotely as volunteer on a distributed open source project.}
		\item {Learned how to work in a internationalization process of a software and lead a team of translators.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
